Issues with Dynamical Measurements Across the Disk

### 2019-03-21 paper/ms.tex
Add ref to new paper

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the
era of {\em Gaia} DR2. Recent major discoveries include the remnants of a
major merger
\citep{2018ApJ...860L..11K,2018Natur.563...85H,2018arXiv180704290L,2019MNRAS.482.3426M},
a phase-space ``spiral'' in the solar neighborhood \citep{2018Natur.561..360A} possibly indicating either local
substructure infall \citep{2018MNRAS.481.1501B,2018arXiv180800451L} or bar
buckling \citep{2018arXiv181109205K}, and a gap suggestive of perturbation by a dark matter
subtructure in the tidal stream GD1 \citep{2018arXiv181103631B}.
These discoveries all indicate that the Milky Way's stellar distribution, which demonstrably departs significantly from axisymmetry, is undergoing phase mixing and dynamical interactions across a range of spatial and temporal scales.

>>>>

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the
era of {\em Gaia} DR2. Recent major discoveries include the remnants of a
major merger
\citep{2018ApJ...860L..11K,2018Natur.563...85H,2018arXiv180704290L,2019MNRAS.482.3426M},
a phase-space ``spiral'' in the solar neighborhood \citep{2018Natur.561..360A} possibly indicating either local
substructure infall \citep{2018MNRAS.481.1501B,2018arXiv180800451L}, bar
buckling \citep{2018arXiv181109205K}, although may just be contributions from moving groups \citep{2019arXiv190308325M} and a gap suggestive of perturbation by a dark matter
subtructure in the tidal stream GD1 \citep{2018arXiv181103631B}.
These discoveries all indicate that the Milky Way's stellar distribution, which demonstrably departs significantly from axisymmetry, is undergoing phase mixing and dynamical interactions across a range of spatial and temporal scales.
